Discrete Quantum Theories and Computing

### 2019-05-23 dissertation.tex
- We do not recommend using alternating page margins as this can cause problems if you opt to print the final version. We recommend changing your margins to one inch on all four sides. This margin space is satisfactory for ProQuest publications. You are not required to make this change but we highly recommend it.
- On the title page, list your name as "Yu-Tsung Tai" (rather than "Tai, Yu-Tsung"

- On the abstract page, list your name as "Yu-Tsung Tai" (rather than "Tai, Yu-Tsung"
- Your table of contents is currently in a font with all capital letters. Please change this to a font with the sta

%% LyX 2.3.2-2 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[11pt,twoside]{iuphd}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{fontspec}
\setmainfont[Mapping=tex-text]{Times New Roman}
\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}
\usepackage{verbatim}
\usepackage{rotfloat}
\usepackage{booktabs}
\usepackage{mathrsfs}
\usepackage{url}
\usepackage{enumitem}
\usepackage{pdfpages}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage[all]{xy}

@@

\usepackage{polyglossia}
\setdefaultlanguage[variant=american]{english}
\setotherlanguage{arabic}
\setotherlanguage{bahasai}
\setotherlanguage{basque}
\setotherlanguage{french}
\setotherlanguage{german}
\setotherlanguage{italian}
\setotherlanguage{portuges}
\setotherlanguage{turkish}
\setotherlanguage{vietnamese}
\usepackage[style=numeric-comp,maxbibnames=10,doi=false,isbn=false,url=false]{biblatex}
\addbibresource{prop.bib}
\begin{document}
\title{Discrete Quantum Theories and Computing}
\author{Tai, Yu-Tsung}

@@

\subsection{Explicit generalization of the Hopf fibration construction\label{subsec:Explicit-generalization-of}}

@@

\section{The geometry of entanglement\label{sec:The-geometry-of}}

@@

\subsection{Counting states on the discrete Bloch sphere}

@@

\subsection{Maximal entanglement\label{subsec:Maximal-entanglement}}

@@

\subsection{Discrete Deutsch algorithm\label{subsec:Discrete-Deutsch-algorithm}}

@@

\subsection{Classical Choquet integrals and Expectation Values of Observables}

>>>>

%% LyX 2.3.2-2 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[11pt]{iuphd}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{fontspec}
\setmainfont[Mapping=tex-text]{Times New Roman}
\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}
\usepackage{verbatim}
\usepackage{rotfloat}
\usepackage{booktabs}
\usepackage{mathrsfs}
\usepackage{url}
\usepackage{enumitem}
\usepackage{pdfpages}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage[all]{xy}

@@

\usepackage{polyglossia}
\setdefaultlanguage[variant=american]{english}
\setotherlanguage{arabic}
\setotherlanguage{bahasai}
\setotherlanguage{basque}
\setotherlanguage{french}
\setotherlanguage{german}
\setotherlanguage{italian}
\setotherlanguage{portuges}
\setotherlanguage{turkish}
\setotherlanguage{vietnamese}
\usepackage[style=numeric-comp,maxbibnames=10,doi=false,isbn=false,url=false]{biblatex}
\addbibresource{prop.bib}
\begin{document}
\title{Discrete Quantum Theories and Computing}
\author{Yu-Tsung Tai}

@@

\subsection{Explicit Generalization of the Hopf Fibration Construction\label{subsec:Explicit-generalization-of}}

@@

\section{The Geometry of Entanglement\label{sec:The-geometry-of}}

@@

\subsection{Counting States on the Discrete Bloch Sphere}

@@

\subsection{Maximal Entanglement\label{subsec:Maximal-entanglement}}

@@

\subsection{Discrete Deutsch Algorithm\label{subsec:Discrete-Deutsch-algorithm}}

@@

\subsection{Classical Choquet Integrals and Expectation Values of Observables}
